|

### 2021-02-14 appendix/appendix.Rmd
small changes in the text

We ran our survey experiments from October 30 to December 14 via Qualtrics. Our
sample includes `r nrow(df1)` Brazilians older than 18 years of age from the
five regions of the country (Center-West, North, Northeast, South, and
Southeast). We used quotas for gender and region to ensure that our sample was
similar to the Brazilian population in those characteristics. We also collected
information about whether the subjects had been victimized in the previous 12
months, as well as their opinion the Brazilian judicial system and the police
forces. They follow in the graphs and tables below.

@@

About 98% of the interviewees agreed to participate in the survey experiment.
We therefore exclude the remaining cases from the dataset.

@@

We asked subjects whether they had victimized in the previous 12 months, as
crime victims may be more likely to support lynchings. The responses follow
below.

@@

We also estimate AMCE coefficients for our conjoint experiment. This method
selects one reference category for each attribute and look at changes from the
baseline level. The reference category are marked as zero in our models.

@@

Results do not seem to vary according to the gender of the respondent. We focus
here on the differences between males and females and exclude the 11
observations in which respondents preferred not to say their gender or marked
"other" in our questionnaire. Across all conjoint experiment attributes, we see
that an overlap between the 95% confidence intervals for males and females.

@@

We also disaggregate the results by monthly household income. As some
categories have few respondents, we group them into three categories: (i) up to
R\$3,000 (US\$550); (ii) from R\$3,001 to R\$5,000 (US\$550-915); and (iii)
above R\$5,000 (US\$915+). The levels roughly represent low, middle, and
high-income households. We find no considerable difference amongst them.

@@

Here we assess whether subjects who support the death penalty have different
preferences towards lynching victims. There are fewer respondents who answered
"Don't Know" or "Rather Not Say" to our question, so the confidence intervals
from their estimates are larger than the for the other two categories. The
estimates largely overlap across the four groups, although those who answered
"Rather Not Say" are less favorable to lynching Indigenous criminals.

@@

Experimental results do not change when we break the responses according to how
subjects view the police forces.

@@

In addition to the conjoint experiments, we also asked respondents to justify
their profile choices. We added a textbook after each conjoint and informed
subjects that their responses were optional. However, we obtained `r (nrow(df1) - sum(is.na(df1$q13_text))) + (nrow(df1) - sum(is.na(df1$q14_text))) + (nrow(df1) - sum(is.na(df1$q15_text))) + (nrow(df1) - sum(is.na(df1$q16_text))) + (nrow(df1) - sum(is.na(df1$q17_text)))` responses
in our survey, which we analyze here.

@@

We also construct a feature co-occurrence matrix (FCM) that shows which words
appear together in the responses we collected. Again, the results confirm the
findings of the conjoint experiment. As suggested in the previous graph, we see
a central cluster that describe crime and victim characteristics and includes
the words _linchamentos_ (lynchings), _caso_ (case), _estupro_ (rape),
_criança_ (child), _assassinato_ (murder), and _vítima_ (victim). This
highlights that these are the most important reasons why respondents choose
lynching profiles.

@@

We estimate a latent Dirichlet allocation (LDA) model to identify the three
most important topics in our corpus. The first topic includes words that refer
to victim and crime characteristics, many of which have also appeared in our
previous estimations. Some of the most common words in this group are _crime_
(crime), _criança_ (child), _estupro_ (rape), _vítima_ (victim), _porque_
(because), _idoso_ (elderly), _grave_ (serious), and _molestar_ (molest). When
we count the number of topics in the corpus, we see that this is the
predominant one. The second topic identified by the model describes lynching
perpetrators, as it contains the words like _polícia_ (police), _pessoas_
(people), and _família_ (family). The third topic identifies the same words we
associate with respondents who are against lynchings, such as _nenhum_ (none),
_opção_ (choice), _não_ (no), and _contra_ (against). As our results show,
respondents decide which individual deserves punishment based on factors
related to the crime he/she committed, specially the crime victim. There is
also a group of respondents that oppose lynchings in principle, who affirm that
lynchings are never justified.

@@

Before each vignette, respondents will read the following text:

@@

After the vignette, respondents will be presented with this question:

* Would you think that the lynching was justified? Please use the slider below
  to indicate your opinion. For disagreement, use 0 to 49; for agreement,
  use 51 to 100. Please use 50 if you neither agree nor
  disagree.[^vig02-exp02]

@@

Table \ref{tab:exp02main} summarizes our results. As we see, none of the
treatment effects are statistically significant at conventional levels. This
indicates that institutional factors do not affect lynching support in our
sample.

@@

We do not find considerable heterogeneity in the these results. Overall, the
three treatment conditions are very stable, thus we are confident that the
main results are not driven by any particular group.

>>>>

We ran our survey experiments from October 30 to December 14 via Qualtrics. Our
sample includes `r nrow(df1)` Brazilians older than 18 years of age from the
five regions of the country (Center-West, North, Northeast, South, and
Southeast). We used quotas for gender and region to ensure that our sample was
similar to the Brazilian population in those characteristics. We also collected
information about whether the subjects had been victimized in the previous 12
months, as well as their opinion of the Brazilian judicial system and the
police forces. They follow in the graphs and tables below.

@@

About 98% of the interviewees agreed to participate in the survey experiment.
We excluded respondents who did not give their consent from the dataset.

@@

We asked subjects whether they had been victimized in the previous 12 months,
as crime victims may be more likely to support lynchings. The responses follow
below.

@@

We also estimate AMCE coefficients for our conjoint experiment. This method
selects one reference category for each attribute and looks at changes from the
baseline level. The reference categories are marked as zero in our models.

@@

Results do not seem to vary according to the gender of the respondent. We focus
here on the differences between males and females and exclude the 11
observations in which respondents preferred not to say their gender or marked
"other" in our questionnaire. Across all conjoint experiment attributes, we see
an overlap between the 95% confidence intervals for males and females.

@@

We also disaggregate the results by monthly household income. As some
categories have few respondents, we group them into three categories: (i) up to
R\$3,000 (US\$550); (ii) from R\$3,001 to R\$5,000 (US\$550-915); and (iii)
above R\$5,000 (US\$915+). The levels roughly represent low, middle, and
high-income households. We find no considerable differences among them.

@@

Here we assess whether subjects who support the death penalty have different
preferences towards lynching victims. There are fewer respondents who answered
"Don't Know" or "Rather Not Say" to our question, so the confidence intervals
from their estimates are larger than for the other two categories. The
estimates largely overlap across the four groups, although those who answered
"Rather Not Say" are less favorable to lynching Indigenous criminals.

@@

Experimental results do not change when we break down the responses according
to how subjects view the police forces.

@@

In addition to the conjoint experiments, we also asked respondents to justify
their profile choices. We added a text box after each conjoint and informed
subjects that their responses were optional. However, we obtained `r (nrow(df1) - sum(is.na(df1$q13_text))) + (nrow(df1) - sum(is.na(df1$q14_text))) + (nrow(df1) - sum(is.na(df1$q15_text))) + (nrow(df1) - sum(is.na(df1$q16_text))) + (nrow(df1) - sum(is.na(df1$q17_text)))` responses
in our survey, which we analyze here.

@@

We also construct a feature co-occurrence matrix (FCM) that shows which words
appear together in the responses we collected. Again, the results confirm the
findings of the conjoint experiment. As suggested in the previous graph, we see
a central cluster that describes crime and victim characteristics and includes
the words _linchamentos_ (lynchings), _caso_ (case), _estupro_ (rape),
_criança_ (child), _assassinato_ (murder), and _vítima_ (victim). This
highlights that these are the most important reasons why respondents choose
lynching profiles.

@@

We estimate a latent Dirichlet allocation (LDA) model to identify the three
most important topics in our corpus. The first topic includes words that refer
to victim and crime characteristics, many of which have also appeared in our
previous estimations. Some of the most common words in this group are _crime_
(crime), _criança_ (child), _estupro_ (rape), _vítima_ (victim), _porque_
(because), _idoso_ (elderly), _grave_ (serious), and _molestar_ (molest). When
we count the number of topics in the corpus, we see that this is the
predominant one. The second topic identified by the model describes lynching
perpetrators, as it contains the words like _polícia_ (police), _pessoas_
(people), and _família_ (family). The third topic identifies the same words we
associate with respondents who are against lynchings, such as _nenhum_ (none),
_opção_ (choice), _não_ (no), and _contra_ (against). As our results show,
respondents decide which individual deserves punishment based on factors
related to the crime he/she committed, especially the crime victim. There is
also a group of respondents that oppose lynchings in principle, who affirm that
lynchings are never justified.

@@

Before each vignette, respondents read the following text:

@@

After the vignette, respondents were presented with this question:

* Do you think that the lynching was justified? Please use the slider below
  to indicate your opinion. For disagreement, use 0 to 49; for agreement,
  use 51 to 100. Please use 50 if you neither agree nor
  disagree.[^vig02-exp02]

@@

Table \ref{tab:exp02main} summarizes our results. As we see, none of the
treatment effects are statistically significant at conventional levels. This
suggests that institutional factors do not affect lynching support in our
sample.

@@

We do not find considerable heterogeneity in the results. Overall, the
three treatment conditions are very stable, thus we are confident that the
main results are not driven by any particular group.
